Report - June 2017

### 2017-08-24 report.Rmd

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
ds_forecast = forecast_viz(obs_data = obs_data_newmoon,
               obs_date_col_name = "NewMoonNumber",
               obs_val_col_name = 'DS',
               for_data = for_data,
               for_date_col_name = "NewMoonNumber",
               for_val_col_name = "estimate",
               for_model_name = "ensemble",
               for_lowerpi_col_name = "LowerPI",
               for_upperpi_col_name = "UpperPI",
               start_newmoon = 300)
  plot(ds_forecast)

>>>>

data = compile_forecasts()
ensemble = dplyr::filter(data, level == 'All', model == 'Ensemble', date == max(date))
sp_predictions = get_sp_predicts(ensemble, 'All', lead_time = 1)
ds_forecast = forecast_viz(obs_data = obs_data_newmoon,
               obs_date_col_name = "newmoonnumber",
               obs_val_col_name = 'DS',
               for_data = for_data,
               for_date_col_name = "newmoonnumber",
               for_val_col_name = "estimate",
               for_model_name = "ensemble",
               for_lowerpi_col_name = "LowerPI",
               for_upperpi_col_name = "UpperPI",
               start_newmoon = 300)
  plot(ds_forecast)
